VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-10 paper/background.tex
first paragraph of background ready

Supplying power to tiny embedded computers using batteries alone is not sustainable. Batteries are a great pollutant. A solution is to replace batteries with smaller, but more environment friendly capacitors and supply power directly from the ambient energy sources.

What platforms enable intermittent computation: WISP~\cite{} (with its variants such as WISPCam~\cite{}), Moo~\cite{}, ambient backscatter~\cite{}, or computation RFID commercial platforms such as~\cite{}. In case of the above platforms, the main source of energy is electromagnetic radiation in the radio frequency range.

Application include long-term battery-less monitoring. One example is the distributed monitoring of moisture of large plant fields during vegetation~\cite{}. Other applications include battery-less image capture and processing~\cite{}, distributed low-power networking~\cite{}.

>>>>

Supplying power to tiny embedded computers using batteries alone is not sustainable. European Commission estimates that more than 160 kilotons of consumer batteries enter the European Union annually~\cite{eu_batteries_2016}. Since not all batteries are properly recycled, they constitute a potential environmental hazard. A potent solution is to replace batteries with smaller, but more environment friendly (super-)capacitors (promising millions of charge/discharge cycles~\cite[Sec. I]{ongaro_pwre_2012}) and to supply them directly from the ambient energy sources. The limitation of the capacitor as storage is lower energy density than battery, making effective capacitor discharge times orders of magnitude smaller than for battery.

Many platforms already enable intermittent computation: WISP~\cite{} (with its variants such as WISPCam~\cite{}), Moo~\cite{moo}, ambient backscatter~\cite{liu_sigcomm_2013}, or computation RFID commercial platforms such as~\cite{}. In case of the above platforms, the main source of energy is electromagnetic radiation in the radio frequency range. Naturally, other forms of energy harvesting exist, The reader is refered to extensive surveys~\cite{}.

Application include long-term battery-less monitoring. One example is the distributed monitoring of moisture of large plant fields during vegetation~\cite{}. Other applications include battery-less image capture and processing~\cite{}, distributed low-power networking~\cite{} or implantable sensors~\cite{rodriguez_tbcs_2015}.
